### 2020-03-08 short.body.tex
new fig

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
The solid, white lines represent the contours.
The solid, red lines represent the example scenario that assumes $p = 0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
The solid, red circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
\label{fig.relevance}}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
The white lines represent the contours.
The white circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
\label{fig.relevance}}
\end{center}
\end{figure*}
